---
title: "Hw4"
author: "MariaRomanova"
output: pdf_document
---
## First of all raw data is needed, and assume that file in current directory 
```{r}
weather = readRDS('./weather.rds')
```
## Quick look at the data:
###1 Measure column looks unnormal (X* variables must be days)
###2 All X* columns are of class character
###3 There are not complete cases with NA data

```{r}
head(weather, 10)
sum(complete.cases(weather))
summary(weather)
sum(duplicated(weather))
```
## Library will be tidyr and stringr
```{r}
library(stringr)
library(tidyr)
library(dplyr)
```
## It seems wrong that months and years are rows and days are colunms, and logicaly it should be columns: days, months, years, and then all measures; rows: measured data
```{r}
weather <- gather(weather, day, data, colnames(weather[5:35]))
```

```{r}
weather <- weather[,-1]
weather <- spread(weather, key = measure, value = data)
```
```{r,error=FALSE}
weather <- weather %>% 
  mutate(day = extract_numeric(day))
```

```{r}
weather <- arrange(weather, year, month,day)
```

### Get rid of 'T' in PrecipitationIn collumn and replace with NA
```{r}
weather$PrecipitationIn <- gsub('T', NA, weather$PrecipitationIn)
```
### Next changing of class to numeric

```{r}
weather[,-5] <- lapply(weather[,-5], as.numeric)
weather$Events <- as.factor(weather$Events)
```




### Piece of code can be used for delete full empty rows we can also use na.omit but not full NA rows will be deleted as well
```{r}
vec = c()
f=1
for(i in 1:length(weather$month)){
  if (sum(is.na(weather[i,4:25])) == 22){
    vec[f] <- i
    f <- f+1
  } 
}
weather <- weather[-c(vec),]
```
### And one more code which will replace blanck rows in column, because if later on this raws will needed to be omited that can be usefull, but it is optional
```{r}
for (i in 1:length(weather$Events)){
  if (!grepl('^.', weather$Events[i])){
    weather$Events[i] <- NA
  }
}
```

